Efficient Management of Reified Statements in RDF

### 2012-06-07 trunk/paper-iswc-reification/querying.tex
further clarification in the querying section

\noindent
% \removable{As usual, each valuation $\eta \in \fctEvalPlus{P}{G}$ is called a \emph{solution} for $P$ in $G$.}
% 
We emphasize that our definitions in this section resemble the definitions with which
	%P\'{e}rez et al.~define
the evaluation function $\fctEval{\cdot}{ }$ for ordinary SPARQL
	%expressions~\cite{Perez09:SemanticsAndComplexityOfSPARQL}.
	expressions is defined~\cite{Perez09:SemanticsAndComplexityOfSPARQL}.
As the primary difference we note that the definitions for SPARQL are based on so called \emph{solution mapping}s, that are, partial mappings $\mu : \symAllVariables \rightarrow \symAllURIs \cup \symAllBNodes \cup \symAllLiterals$, whereas we use valuations $\eta : \symAllVariables \rightarrow \symAllTriples \cup \symAllURIs \cup \symAllBNodes \cup \symAllLiterals$. However, any valuation
	%$\eta$ for which $\forall \, ?v \in \fctDom{\eta} : \eta(?v) \notin \symAllTriples$,
	that binds variables only to URIs, blank nodes, or literals (but not to {\RDFplusTriple}s),
may also be understood as a solution mapping. Based on this understanding, the following result shows that our query semantics for {\SPARQLplus} is fully compatible to the usual SPARQL semantics (defined in~\cite{Perez09:SemanticsAndComplexityOfSPARQL}), that is, any system that supports {\RDFplus} and {\SPARQLplus} may use {\SPARQLplus} semantics to answer (ordinary) SPARQL expressions over (ordinary) RDF graphs.

@@

In addition to the {\SPARQLplus} semantics defined in the previous section, we now define
	%an alternative semantics for {\SPARQLplus}. This alternative semantics
	a function for converting {\SPARQLplus} queries to SPARQL queries. This conversion function
enables RDF systems that support the ordinary RDF data model (but not our {\RDFplus} data model), to answer {\SPARQLplus} queries.

@@

\noindent
The following result is a direct consequence of Propositions~\ref{Proposition:EquivalenceOfSemantics}, \ref{Proposition:EquivalenceOfSyntaxAfterConverting}, and~\ref{Proposition:QueryEquivalenceAfterConverting}:
\begin{corollary}
	For any {\RDFplusGraph} $G$ and any {\SPARQLplus} expression $P$ that does not contain a sub-expression
		\removable{of the form}
	$(tp \OpAS ?v)$ it holds $\fctEvalPlus{P}{G} = \pi_{\fctVarsPlus{P}}\bigl( \fctEval{P'}{\fctDescent{G}} \bigr)$ where $P'$ is an arbitrary RDF compatible expression $\fctDescentWP{w}{P}$ of $P$.
\end{corollary}

\noindent
\todo{briefly discuss the Corollary}

>>>>

\noindent
% \removable{As usual, each valuation $\eta \in \fctEvalPlus{P}{G}$ is called a \emph{solution} for $P$ in $G$.}
% 
We emphasize that our definitions in this section resemble the definitions with which
	%P\'{e}rez et al.~define
the evaluation function
	%$\fctEval{\cdot}{ }$
	$\fctEval{P}{G}$
for ordinary SPARQL
	%expressions~\cite{Perez09:SemanticsAndComplexityOfSPARQL}.
	expressions is defined~\cite{Perez09:SemanticsAndComplexityOfSPARQL}.
As the primary difference we note that the definitions for SPARQL are based on so called \emph{solution mapping}s, that are, partial mappings $\mu : \symAllVariables \rightarrow \symAllURIs \cup \symAllBNodes \cup \symAllLiterals$, whereas we use valuations $\eta : \symAllVariables \rightarrow \symAllTriples \cup \symAllURIs \cup \symAllBNodes \cup \symAllLiterals$. However, any valuation
	%$\eta$ for which $\forall \, ?v \in \fctDom{\eta} : \eta(?v) \notin \symAllTriples$,
	that binds variables only to URIs, blank nodes, or literals (but not to {\RDFplusTriple}s),
may also be understood as a solution mapping. Based on this understanding, the following result shows that our query semantics for {\SPARQLplus} is backwards compatible w.r.t.~the usual SPARQL semantics (%
	%as defined
in~\cite{Perez09:SemanticsAndComplexityOfSPARQL}), that is, any system that supports {\RDFplus} and {\SPARQLplus} may use {\SPARQLplus} semantics to answer (ordinary) SPARQL expressions over (ordinary) RDF graphs.

@@

In addition to the {\SPARQLplus} semantics defined in the previous section, we now define an approach for answering {\SPARQLplus} queries using the usual SPARQL semantics. This approach is based on a function for converting {\SPARQLplus} queries to SPARQL queries.

@@

\noindent
The following result is a direct consequence of Propositions~\ref{Proposition:EquivalenceOfSemantics}, \ref{Proposition:EquivalenceOfSyntaxAfterConverting}, and~\ref{Proposition:QueryEquivalenceAfterConverting}:

\begin{corollary} \label{Corollary:EquivalenceSPARQLplusAndSPARQL}
	For any {\RDFplusGraph} $G$ and any {\SPARQLplus} expression $P$ that does not contain a sub-expression
		\removable{of the form}
	$(tp \OpAS ?v)$ it holds $\fctEvalPlus{P}{G} = \pi_{\fctVarsPlus{P}}\bigl( \fctEval{P'}{\fctDescent{G}} \bigr)$ where $P'$ is an arbitrary RDF compatible expression $\fctDescentWP{w}{P}$ of $P$.
\end{corollary}

\noindent
The importance of Corollary~\ref{Corollary:EquivalenceSPARQLplusAndSPARQL} lies in providing an alternative approach for answering {\SPARQLplus} queries (without $\OpAS$\!) that is based on the usual SPARQL semantics only. This approach presents an easy implementable interim solution for supporting {\SPARQLplus} in existing SPARQL execution systems before they are upgraded to our {\RDFplus} data model.
